The CMS Data Aggregation System

### 2010-05-04 doc/paper.tex
Adding Simon's cache and analytics picture, since it's better describe cache/analytics flow. Change text wrt that.
git-svn-id: svn+ssh://svn.cern.ch/reps/CMSDMWM/DAS/trunk@1514 4525493e-7705-40b1-a816-d608a930855b

\subsection{Caching system}
The DAS caching system was divided into two different caches: raw-cache and hot-cache.
The purpose of raw-cache was to store results coming from data services for
as long as specified in data-service response header. While the purpose of hot-cache
was to keep final DAS results corresponding to provided user query. We use a populator
services (jobs) to feed raw-cache with highly requested queries. Here we will only
discuss the raw-cache organization. 
\begin{figure}[htb]
\centering
\includegraphics[width=150mm]{DAS_cache.pdf}
\caption{
DAS cache system.
}
\label{DAS_cache}
\end{figure}
As it shown in figure \ref{DAS_cache} we setup
dedicated DAS cache request server to manage user requests. Each request placed into
queue who was used by workers to spawn a data-service request. 
This allows us to utilze a multi-core technology and place a workers at each 
core.\footnote{A number of workers per core were adjustable to satisfy requests load.}
Each worker talk to DAS raw-cache and either stored mapped results over there or merge
them with existing data object in DAS cache. We evaluated several technologies
as a choice for DAS cache back-end, including relational MySQL DB \cite{MySQL} 
and object oriented CouchDB \cite{CouchDB} and MongoDB \cite{MongoDB}.
Each of this technologies had its own pros and cons. For instance usage
of MySQL provided a SQL queries (as in federated DBs, see \cite{FedDB}), but
required auto-schema generation on a fly.\footnote{We did not apply any
restriction to DAS QL and did not know in advance what our users will be
querying.} While, using CouchDB and MongoDB, we were able to store
data-service output naturally as data objects into DB. Finally we decided
to use MongoDB due to its flexible and
powerful querying syntax, which were easy to map into DAS QL expressions.

>>>>

\subsection{Caching system}
The DAS caching system was divided into two different caches: raw-cache and hot-cache.
The purpose of raw-cache was to store results coming from data services for
as long as specified in data-service response header. While the purpose of hot-cache
was to keep final DAS results corresponding to provided user query. We use a populator
services (jobs) to feed raw-cache with highly requested queries. Here we will only
discuss the raw-cache organization. 
\begin{figure}[htb]
\centering
\includegraphics[width=150mm]{DAS_Cache_and_Analytics.pdf}
\caption{
DAS cache system.
}
\label{DAS_cache}
\end{figure}
As it shown in figure \ref{DAS_cache} the DAS cache server has dual purpose.
On one side it talks to DAS Analytics DB to trigger jobs for worker robot
who update cache with most popular queries, on another it talks to DAS
raw-cache back-end to either stored mapped results or merge them with 
existing DAS objects in a cache. We should note that we use on-demand
approach to answer user queries, but at the same time with a help of
DAS Analytics DB we force worker robots (populators) to pre-fetch
the most popular queries up-front.

We evaluated several technologies
as a choice for DAS cache back-end, including relational MySQL DB \cite{MySQL} 
and object oriented CouchDB \cite{CouchDB} and MongoDB \cite{MongoDB}.
Each of them had its own pros and cons. For instance usage
of MySQL provided a SQL queries (as in federated DBs, see \cite{FedDB}), but
required auto-schema generation on a fly.\footnote{We did not apply any
restriction to DAS QL and did not know in advance what our users will be
querying.} While, using CouchDB and MongoDB, we were able to store
data-service output naturally as documents objects into DB. Finally we decided
to use MongoDB due to its flexible and
powerful querying syntax, which were easy to map into DAS QL expressions.
